\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{tikz}
\usepackage[margin=1in]{geometry}

\begin{document}

%========= Preamble (this is prepended to each question by the importer) =========
\begin{center}
\begin{tikzpicture}[x=1cm,y=1cm]
  % Column titles
  \node[font=\Large] at (1.5,5.0) {Strep Throat};
  \node[font=\Large] at (4.5,5.0) {Healthy};

  % Outer 2x2 box and dividers
  \draw[line width=1pt] (0,0) rectangle (6,4);
  \draw[line width=1pt] (3,0) -- (3,4);
  \draw[line width=1pt] (0,2) -- (6,2);

  % Cell counts
  \node at (1.5,3) {35};
  \node at (4.5,3) {25};
  \node at (1.5,1) {5};
  \node at (4.5,1) {435};

  % Row labels (left of box)
  \node[anchor=east,align=right] at (-0.6,3) {Positive\\test};
  \node[anchor=east,align=right] at (-0.6,1) {Negative\\test};

  % Row totals (to the right of box)
  \node[anchor=west] at (6.6,3) {60};
  \node[anchor=west] at (6.6,1) {440};

  % Column totals (below box)
  \node at (1.5,-0.8) {40};
  \node at (4.5,-0.8) {460};
\end{tikzpicture}
\end{center}

\bigskip
%===============================================================================

\begin{enumerate}[label=\textbf{S\arabic*.}]

% --- S1 ------------------------------------------------------------------------
\item \textbf{Predictive value.} What is the probability that a person has strep
throat \emph{and} tests positive? \answer{B}

\textit{Use the same table above.}

\begin{enumerate}
  \item $\dfrac{35}{500}$
  \item $\dfrac{35}{60}$
  \item $\dfrac{35}{40}$
  \item $\dfrac{35}{35+25+5}$
  \item $\dfrac{35+25+5}{500}$
\end{enumerate}

% --- S2 ------------------------------------------------------------------------
\item \textbf{False-positive rate.} What is the probability of testing positive
\emph{given} that the person does \emph{not} have strep throat? \answer{A}

\textit{Use the same table above.}

\begin{enumerate}
  \item $\dfrac{25}{460}$
  \item $\dfrac{25}{60}$
  \item $\dfrac{35}{40}$
  \item $\dfrac{25}{500}$
  \item $\dfrac{35+25+5}{500}$
\end{enumerate}

% --- S3 ------------------------------------------------------------------------
\item \textbf{Sensitivity.} What is the probability of testing positive
\emph{given} that the person \emph{has} strep throat? \answer{D}

\textit{Use the same table above.}

\begin{enumerate}
  \item $\dfrac{35+25+5}{500}$
  \item $\dfrac{35}{35+25+5}$
  \item $\dfrac{35}{500}$
  \item $\dfrac{35}{60}$
  \item $\dfrac{35}{40}$
\end{enumerate}

% --- S4 ------------------------------------------------------------------------
\item \textbf{Specificity.} What is the probability of testing negative
\emph{given} that the person does \emph{not} have strep throat? \answer{E}

\textit{Use the same table above.}

\begin{enumerate}
  \item $\dfrac{5}{40}$
  \item $\dfrac{35}{60}$
  \item $\dfrac{35+5+435}{500}$
  \item $\dfrac{435}{500}$
  \item $\dfrac{435}{460}$
\end{enumerate}

% 5 --------------------------------------------------------------------------
\item In a 1974 ``Dear Abby'' letter, a woman lamented that she had just given
birth to her eighth child and all were girls. Her doctor had assured her that
the chance of the eighth child being a girl was less than $1$ in $100$.
What is the real probability that the eighth child would be a girl?
\begin{enumerate}
  \item $0.0039$
  \item $0.5$
  \item $(0.5)^{7}$
  \item $(0.5)^{8}$
  \item $\dfrac{(0.5)^{7}+(0.5)^{8}}{2}$
\end{enumerate}

% 6 --------------------------------------------------------------------------
\item Hospital A has about 20 births per day, and Hospital B has about 40 births
per day. About 50\% of all babies are boys, but the percentage who are boys
varies at each hospital from day to day. Over the course of a year, which
hospital will have more days on which 60\% or more of the births are boys?
\begin{enumerate}
  \item Hospital A
  \item Hospital B
  \item The difference will be negligible.
  \item By the law of small numbers, this cannot be predicted.
  \item By the law of large numbers, this cannot be predicted.
\end{enumerate}

% 7 --------------------------------------------------------------------------
\item The probability that a college's mathematics department will fill an opening
with a female professor is $0.55$, while the probability that the physics
department will fill an opening with a female professor is $0.3$.
Assuming independence, what is the probability that \emph{exactly one}
of these two departments will fill their position with a female professor?
\begin{enumerate}
  \item $(0.55)(0.3)$
  \item $0.55+0.3-(0.55)(0.3)$
  \item $0.55-(0.55)(0.3)$
  \item $(0.55)(0.70)+(0.30)(0.45)$
  \item $(0.55)(0.70)+(0.30)(0.45)-(0.55)(0.30)$
\end{enumerate}

% 8 --------------------------------------------------------------------------
\item Suppose that 2\% of a clinic's patients are known to have cancer.
A blood test is positive in 98\% of patients with cancer but is also positive
in 3\% of patients who do not have cancer.
If a randomly chosen patient tests positive, what is the probability
that the person actually has cancer?
\begin{enumerate}
  \item $0.02$
  \item $0.02+0.03$
  \item $(0.02)(0.98)$
  \item $(0.02)(0.98)+(0.98)(0.03)$
  \item $\displaystyle
          \frac{0.02\cdot0.98}{\,0.02\cdot0.98+0.98\cdot0.03\,}$
\end{enumerate}

% 9 --------------------------------------------------------------------------
\item A teacher has 90 students. Of those, 21 have at least two analog clocks
in their homes, and 62 have at least three television sets in their homes.
There are 15 students who do not have at least two analog clocks and do not have
at least three television sets. Let $C$ be the event “at least two analog clocks”
and $T$ the event “at least three television sets”.
Are $C$ and $T$ mutually exclusive events?
\begin{enumerate}
  \item No, because $P(C\cap T)=\dfrac{8}{90}$.
  \item No, because $P(C\cap T)=\dfrac{75}{90}$.
  \item No, because $P(C\cap T)=\dfrac{83}{90}$.
  \item Yes, because $P(C\cap T)=\dfrac{8}{90}$.
  \item Yes, because $P(C\cap T)=\dfrac{83}{90}$.
\end{enumerate}

% 10 -------------------------------------------------------------------------
\item A random sample of adults aged 25 and up were surveyed as to whether or not
they had tattoos and whether or not they had ever taken a college course.
The mosaic plot below displays the data.

\begin{center}
\begin{tikzpicture}[x=0.08cm,y=0.08cm,baseline]
  % total frame (width 140, height 80 for easy ratios)
  \draw (0,0) rectangle (140,80);
  % column split (adjust 65/75 if you want different column totals)
  \draw (65,0) -- (65,80);
  % row splits within each column (adjust 48 and 30 to change row proportions)
  \draw (0,48) -- (65,48);     % left column horizontal split
  \draw (65,30) -- (140,30);   % right column horizontal split

  % subtle shading to differentiate blocks (tune to taste)
  \fill[gray!25] (0,48) rectangle (65,80);    % No tattoos (left–top)
  \fill[gray!12] (65,0) rectangle (140,30);   % Tattoos (right–bottom)

  % labels inside/under
  \node at (32.5,64) {\small No tattoos};
  \node at (102.5,15) {\small Tattoos};

  \node[below] at (32.5,0) {\small No college};
  \node[below] at (102.5,0) {\small At least some college};
\end{tikzpicture}
\end{center}

Which is greater, the probability that someone in this sample has taken a college
course \emph{given} that they have a tattoo, or the probability that someone has
a tattoo \emph{given} that they have taken a college course?
\begin{enumerate}
  \item The probability of college $\mid$ tattoo is greater.
  \item The probability of tattoo $\mid$ college is greater.
  \item The two probabilities are equal.
  \item This cannot be answered without knowing $P(\text{college and tattoo})$.
  \item This cannot be answered without knowing
        (1) $P(\text{college})$, (2) $P(\text{tattoo})$, and
        (3) $P(\text{college and tattoo})$.
\end{enumerate}

% 11 -------------------------------------------------------------------------
\item For which of the following probability assignments are events $E$ and $F$
independent? (Each row lists $P(E\cap F^{c})$, $P(E\cap F)$, $P(E^{c}\cap F)$;
the remaining cell is $P(E^{c}\cap F^{c})=1$ minus the sum of those three.)
\begin{enumerate}
  \item $0.2,\;0.2,\;0.2$
  \item $0.3,\;0.0,\;0.3$
  \item $0.3,\;0.2,\;0.1$
  \item $0.4,\;0.1,\;0.1$
  \item $0.2,\;0.4,\;0.2$
\end{enumerate}

% 12 -------------------------------------------------------------------------
\item Let
\begin{itemize}
  \item[I.] A randomly selected high school senior eats breakfast.
  \item[II.] A randomly selected \emph{teenager} is a high school senior who eats breakfast.
  \item[III.] A randomly selected teenager who eats breakfast is a high school senior.
\end{itemize}
Which order best compares these probabilities?
\begin{enumerate}
  \item $P(\text{I})<P(\text{II})<P(\text{III})$
  \item $P(\text{I})>P(\text{II})>P(\text{III})$
  \item $P(\text{I})<P(\text{III})<P(\text{II})$
  \item $P(\text{I})>P(\text{III})>P(\text{II})$
  \item $P(\text{II})<P(\text{I})<P(\text{III})$
\end{enumerate}

\end{enumerate}

\end{document}








    









