\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[margin=1in]{geometry}

% --- importer markers (no-ops; your importer looks for them) ---
\newenvironment{asset}[1]{}{}
\newcommand{\uses}[1]{}

\begin{document}

\begin{enumerate}

% 1
\item Which of the following is a true statement? \answer{A}
\begin{enumerate}
  \item The area under a normal curve is always equal to 1, no matter what the mean and standard deviation are.
  \item All bell-shaped curves are normal distributions for some choice of $\mu$ and $\sigma$.
  \item The smaller the standard deviation of a normal curve, the lower and more spread out the graph.
  \item Depending upon the value of the standard deviation, normal curves with different means may be centered around the same number.
  \item Depending upon the value of the standard deviation, the mean and median of a particular normal distribution may be different.
\end{enumerate}

% 2
\item The continuous random variable $X$ has a normal distribution with mean $20$ and standard deviation $4$. For which of the following is the probability equal to $0$? \answer{A}
\begin{enumerate}
  \item $P(X=22)$
  \item $P(X<22)$
  \item $P(X>22)$
  \item $P(21<X<22)$
  \item $P(X<21)\text{ or }P(X>22)$
\end{enumerate}

% 3
\item Populations $P_1$ and $P_2$ are normally distributed and have identical means. However, the standard deviation of $P_1$ is twice the standard deviation of $P_2$. What can be said about the percentage of observations falling within two standard deviations of the mean for each population? \answer{E}
\begin{enumerate}
  \item The percentage for $P_1$ is twice the percentage for $P_2$.
  \item The percentage for $P_1$ is greater than but not twice as great as the percentage for $P_2$.
  \item The percentage for $P_2$ is twice the percentage for $P_1$.
  \item The percentage for $P_2$ is greater than but not twice as great as the percentage for $P_1$.
  \item The percentages are identical.
\end{enumerate}

% 4
\item A trucking firm determines that its fleet of trucks averages a mean of $12.4$ miles per gallon with a standard deviation of $1.2$ miles per gallon on cross-country hauls. What is the probability that one of the trucks averages fewer than $10$ miles per gallon? \answer{B}
\begin{enumerate}
  \item $P\!\left(z<-2.4\right)$
  \item $P\!\left(z<-2\right)$
  \item $P\!\left(z<10\right)$
  \item $P\!\left(z<\dfrac{10}{1.2}\right)$
  \item $P\!\left(z<\dfrac{12.4}{1.2}\right)$
\end{enumerate}

% 5
\item An electronic product takes on average $3.4$ hours to move through an assembly line. If the standard deviation is $0.5$ hours, what is the probability that an item will take between $3$ and $4$ hours to move through the assembly line? \answer{E}
\begin{enumerate}
  \item $P(3<z<4)$
  \item $P\!\left(\dfrac{3}{0.5}<z<\dfrac{4}{0.5}\right)$
  \item $P(3-3.4<z<4-3.4)$
  \item $P\!\left(\dfrac{3-3.4}{\,0.5\,}<z<\dfrac{4-3.4}{\,0.5\,}\right)$
  \item $P\!\left(\dfrac{3-3.4}{0.5}<z<\dfrac{4-3.4}{0.5}\right)$
\end{enumerate}

% 6
\item The mean noise level in a restaurant is $70$ decibels with a standard deviation of $4$ decibels. Ninety-nine percent of the time the noise level is below what value? \answer{E}
\begin{enumerate}
  \item $70+1.96(4)$
  \item $70-2.576(4)$
  \item $70+2.576(4)$
  \item $70-2.326(4)$
  \item $70+2.326(4)$
\end{enumerate}

% 7
\item The mean income per household in a certain state is \$9{,}500 with a standard deviation of \$1{,}750. The middle $95\%$ of incomes are between what two values? \answer{B}
\begin{enumerate}
  \item $9{,}500 \pm 1.645(1{,}750)$
  \item $9{,}500 \pm 1.96(1{,}750)$
  \item $9{,}500 \pm 1.645\!\left(\dfrac{1{,}750}{2}\right)$
  \item $9{,}500 \pm \dfrac{1{,}750}{1.645}$
  \item $9{,}500 \pm \dfrac{1{,}750}{1.96}$
\end{enumerate}

% 8
\item One company produces movie trailers whose mean length is $150$ seconds with a standard deviation of $40$ seconds, while a second company produces movie trailers whose mean length is $120$ seconds with a standard deviation of $30$ seconds. What is the probability that the combined length of two randomly selected trailers, one from each company, will be less than three minutes? \answer{D}
\begin{enumerate}
  \item $0.000$
  \item $P\!\left(z<\dfrac{180-270}{50}\right)$
  \item $P\!\left(z<\dfrac{180-270}{70}\right)$
  \item $P\!\left(z<\dfrac{180-270}{\sqrt{40^2+30^2}}\right)$
  \item $P\!\left(z<\dfrac{180-270}{\sqrt{\tfrac{40^2}{n}+\tfrac{30^2}{n}}}\right)$
\end{enumerate}

% 9
\item Cucumbers grown on a certain farm have weights with a standard deviation of $2$ ounces. What is the mean weight if $85\%$ of the cucumbers weigh less than $16$ ounces? \answer{C}
\begin{enumerate}
  \item $16-0.518(2)$
  \item $16-0.85(2)$
  \item $16-1.036(2)$
  \item $16+0.85(2)$
  \item $16+1.036(2)$
\end{enumerate}

% 10
\item The mean and standard deviation of the sample data collected on a continuous variable $x$ are $10$ and $5$, respectively. The following table shows the relative frequencies of the data in the given intervals. Based on the table, do the data support using a normal model to approximate population characteristics? \answer{D}

\begin{center}
\begin{tabular}{|l|c|}
\hline
\textbf{Interval} & \textbf{Relative frequency} \\
\hline
$-5 \le x < 0$   & $0.03$ \\
$0 \le x < 5$    & $0.12$ \\
$5 \le x < 10$   & $0.35$ \\
$10 \le x < 15$  & $0.34$ \\
$15 \le x < 20$  & $0.14$ \\
$20 \le x < 25$  & $0.02$ \\
\hline
\end{tabular}
\end{center}

\begin{enumerate}
  \item No, because some values are negative.
  \item No, because the relative frequency distribution doesn’t follow the empirical rule.
  \item Yes, because the sum of the relative frequencies is $1.00$.
  \item Yes, because the relative frequency distribution roughly follows the empirical rule.
  \item This cannot be answered without knowing the sample size.
\end{enumerate}

\end{enumerate}

\end{document}
